DCM_investigation

### 2020-10-27 article_figures_ARTHUR_CAPET.Rmd
add light horizons
update light horizons

# add it to complete_tmp2
complete_tmp2 <- cbind(complete_tmp2, light = interpolated_light_data$relative_light, light_absolute = interpolated_light_data$absolute_light)

@@

                            ISOMLD       = min(light, na.rm = TRUE),

@@

                          # just to see
                            ISO_iso1 = try_default(approx(x=depth, y=light, xout=unique(Ziso1b), rule=2)$y,NA, quiet = FALSE)

@@

```{r}

tmp_fitco<- tmp_fitc
tmp_fitco$dcm_or_not[tmp_fitco$shape=="O"]<-1
tmp_fitc[which((tmp_fitc$month<4)|(tmp_fitc$month>10)),c('Zmax','sigmaMAX','DCMratio')]<-NA
tmp_fitco[which((tmp_fitco$month<4)|(tmp_fitco$month>10)),c('Zmax','sigmaMAX','DCMratio','chla_dcm')]<-NA
```

@@

## Absolute light Horizons

@@

tmp_iso1 <- subset(tmp_fitco, select = c('month','ISOMLD','ISOMAX','ISOlow','ISO90B','ISO90T','ISO_iso1' ,'dcm_or_not','year','shape'))

@@

ggplot(tmp_iso, aes(x=month, fill=variable, color=variable)) +
    geom_smooth(aes(y=value),stat = 'summary',
#              fun.data = median_hilow,
              fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.95), alpha=0.5)+
  geom_boxplot(aes(y=value, group=interaction(month,variable)), alpha=0.2, notch = TRUE)+
        scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
  #scale_y_continuous(trans = 'log10') + ylab('[microMoleQuanta/m^2/sec]') +
  ylab('% of Incoming PAR') + theme_bw()  + scale_y_continuous(trans = 'log10') +
      scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal,
                       name="ISO Horizons", 
                       labels=list(TeX('$\\ISO_{MLD}$'),
                                TeX('$\\ISO_{DCM}$'),
                                TeX('$\\ISO_{low}$'),
                                TeX('$\\ISO_{50,bottom}$'),
                                TeX('$\\ISO_{50,top}$'),
                                TeX('$\\ISO_{\\mathrm{PAR}\\,1%}$')))

@@

ggplot(tmp_part, aes(x=month, fill=variable, color=variable)) +
    geom_smooth(aes(y=value),stat = 'summary',
#              fun.data = median_hilow,
              fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.95), alpha=0.5)+
        scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12)) +
        scale_y_continuous(breaks = seq(0,100,10), minor_breaks = NULL) +
    geom_boxplot(aes(y=value, group=interaction(month,variable)), alpha=0.2)+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylab('[%]')+theme_bw()+
  scale_color_brewer(name='Part of tot. Chl:',
                     labels=c('above MLD','within 5m of DCM','above optical depth'),
                     aesthetics = c("colour", "fill"),type = qual ,palette=MyPal)#+ylim(c(0,100))
```

>>>>

# add it to complete_tmp2
complete_tmp2 <- cbind(complete_tmp2, light = interpolated_light_data$relative_light, light_absolute = interpolated_light_data$absolute_light)
#complete_tmp2 <- cbind(complete_tmp2, light = interpolated_light_data$absolute_light)

@@

                            ISOMLD       = try_default(approx(x=depth, y=light, xout=unique(MLD), rule=2)$y,NA, quiet = FALSE),

@@

                            ISO_iso1 = try_default(approx(x=depth, y=light, xout=unique(Ziso1b), rule=2)$y,NA, quiet = FALSE),
                          # Add ABSOLUTE Light levels
                            ISOalow       = try_default(approx(x=depth, y=light_absolute, xout=ZLow, rule=2)$y,NA, quiet = FALSE),
                            ISOa90B       = try_default(approx(x=depth, y=light_absolute, xout=Z90B, rule=2)$y,NA, quiet = FALSE),
                            ISOa90T       = try_default(approx(x=depth, y=light_absolute, xout=Z90T, rule=2)$y,NA, quiet = FALSE),
                            ISOaMLD       = try_default(approx(x=depth, y=light_absolute, xout=unique(MLD), rule=2)$y,NA, quiet = FALSE),
                            ISOaMAX       = try_default(approx(x=depth, y=light_absolute, xout=unique(Zmax), rule=2)$y,NA, quiet = FALSE),
                            ISOaDEMI      = try_default(approx(x=depth, y=light_absolute, xout=unique(Zdemi), rule=2)$y,NA, quiet = FALSE),
                            ISOa_iso1 = try_default(approx(x=depth, y=light_absolute, xout=unique(Ziso1b), rule=2)$y,NA, quiet = FALSE)

@@

```{r}
tmp_fitco<- tmp_fitc
tmp_fitco$dcm_or_not[tmp_fitco$shape=="O"]<-1
tmp_fitc[which((tmp_fitc$month<4)|(tmp_fitc$month>10)),c('Zmax','sigmaMAX','DCMratio')]<-NA
tmp_fitco[which((tmp_fitco$month<4)|(tmp_fitco$month>10)),c('Zmax','sigmaMAX','DCMratio','chla_dcm')]<-NA
```

@@

## Relative & Absolute light Horizons

@@

#relative light
#tmp_iso1 <- subset(tmp_fitco, select = c('month','ISOMLD','ISOMAX','ISOlow','ISO90B','ISO90T','ISO_iso1' ,'dcm_or_not','year','shape'))
tmp_iso1 <- subset(tmp_fitco, select = c('month','ISOMAX','ISOlow','ISO90B','ISO90T','dcm_or_not','year','shape'))

@@

relative_light <- ggplot(tmp_iso, aes(x=month, fill=variable, color=variable)) +
    geom_smooth(aes(y=value),stat = 'summary',
#              fun.data = median_hilow,
#              fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.95), alpha=0.5)+
  geom_boxplot(aes(y=value, group=interaction(month,variable)), alpha=0.2, notch = TRUE)+
        scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
  #scale_y_continuous(trans = 'log10') + ylab('[microMoleQuanta/m^2/sec]') +
  ylab('% of Incoming PAR') + theme_bw()  + scale_y_continuous(trans = 'log10') +
      # scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal,
      #                  name="ISO Horizons", 
      #                  labels=list(#TeX('$\\ISO_{MLD}$'),
      #                           TeX('$\\ISO_{DCM}$'),
      #                           TeX('$\\ISO_{low}$'),
      #                           TeX('$\\ISO_{50,bottom}$'),
      #                           TeX('$\\ISO_{50,top}$')))#,
      #                           #TeX('$\\ISO_{\\mathrm{PAR}\\,1%}$')))
      scale_color_manual(aesthetics = c("colour", "fill"),values = c("#D95F02","#7570B3","#E7298A","#66A61E"), # [1] "#1B9E77" "#D95F02" "#7570B3" "#E7298A" "#66A61E" "#E6AB02" "#A6761D" "#666666"
                       name="ISO Horizons", 
                       labels=list(TeX('$\\ISO_{DCM}$'),
                                TeX('$\\ISO_{low}$'),
                                TeX('$\\ISO_{50,bottom}$'),
                                TeX('$\\ISO_{50,top}$')))

relative_light

#absolute light
tmp_iso1 <- subset(tmp_fitco, select = c('month','ISOaMAX','ISOalow','ISOa90B','ISOa90T','dcm_or_not','year','shape'))

absolute_light <- ggplot(tmp_iso, aes(x=month, fill=variable, color=variable)) +
    geom_smooth(aes(y=value),stat = 'summary',
#              fun.data = median_hilow,
#              fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.95), alpha=0.5)+
  geom_boxplot(aes(y=value, group=interaction(month,variable)), alpha=0.2, notch = TRUE)+
        scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
  scale_y_continuous(trans = 'log10') + ylab('[microMoleQuanta/m^2/sec]') + theme_bw()+
  #ylab('% of Incoming PAR') + theme_bw()  + scale_y_continuous(trans = 'log10') +
      # scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal,
      #                  name="ISO Horizons", 
      #                  labels=list(TeX('$\\ISO_{DCM}$'),
      #                           TeX('$\\ISO_{low}$'),
      #                           TeX('$\\ISO_{50,bottom}$'),
      #                           TeX('$\\ISO_{50,top}$')))
    scale_color_manual(aesthetics = c("colour", "fill"),values = c("#D95F02","#7570B3","#E7298A","#66A61E"), # [1] "#1B9E77" "#D95F02" "#7570B3" "#E7298A" "#66A61E" "#E6AB02" "#A6761D" "#666666"
                       name="ISO Horizons", 
                       labels=list(TeX('$\\ISO_{DCM}$'),
                                TeX('$\\ISO_{low}$'),
                                TeX('$\\ISO_{50,bottom}$'),
                                TeX('$\\ISO_{50,top}$')))

absolute_light

# # https://www.datanovia.com/en/blog/top-r-color-palettes-to-know-for-great-data-visualization/
# library(RColorBrewer)
# display.brewer.pal(n = 8, name = 'Dark2')
# brewer.pal(n=8, name='Dark2')

#grid.arrange(relative_light + theme(legend.position="none"), absolute_light, nrow = 2)
grid.arrange(relative_light, absolute_light, nrow = 2)
```

@@

ggplot(tmp_part, aes(x=month, fill=variable, color=variable)) +
    geom_smooth(aes(y=value),stat = 'summary',
#              fun.data = median_hilow,
              fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.95), alpha=0.5)+
        scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12)) +
        scale_y_continuous(breaks = seq(0,100,10), minor_breaks = NULL) +
    geom_boxplot(aes(y=value, group=interaction(month,variable)), alpha=0.2)+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylab('[%]')+theme_bw()+
  scale_color_brewer(name='Part of tot. Chl:',
                     labels=c('above MLD','within 5m of DCM','above optical depth'),
                     aesthetics = c("colour", "fill"),type = qual ,palette=MyPal)#+ylim(c(0,100))
